### 2015-07-30 bioc192/lect10.tex
finished lecture 11, onto lecture 12

In an enzyme catalysed reaction, substrate binds to the active site and forms a enzyme-substrate complex (ES), which is stabilised by non-covalent interactions.
Note that this interaction is specific.
As the reaction proceeds, transition state (T), which is neither a substrate nor the product, is formed, then proceeds further into enzyme-product complex (EP).
This complex can then be dissociated to form the original enzyme ready for another reactions, and release the product.

>>>>

In an enzyme catalysed reaction, substrate binds to the active site and forms an enzyme-substrate complex (ES), which is stabilised by non-covalent interactions.
Note that this interaction is specific.
As the reaction proceeds, transition state (T), which is neither a substrate nor the product, is formed, then proceeds further into enzyme-product complex (EP).
This complex can then be dissociated to form the original enzyme ready for another reaction, and release the product.
